Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend

### 2024-12-02 paper/paper.qmd
cleaned files

---
title: "Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend"
subtitle: ""
author: 
  - Peter Fan

thanks: "Code and data are available at: [https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books](https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books)."
date: today
date-format: long
abstract: "This study formulates a predictive model to estimate the popularity of children’s books by the reader’s ratings, physical attributes of the books and yearly trend. The study used a dataset of children’s books that were published from the year 1905 to 2020. The generalized linear model with a log-liner link has been used, where the predictors are publication year, years from first publication, cover type, number of pages and average rating by readers, and the predicted variable is the total count of ratings received from readers as an indicator of popularity. The study found that apart from the average rating, the number of pages in the book has a significant effect on the potential popularity, whereas the cover type of the book has no effect. The study suggests that republishing older children’s books can increase the probability of having higher popularity. The low model fit and lack of availability of data regarding the genre and target audience of the book may limit the reliability of the prediction."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend"
subtitle: ""
author: 
  - Peter Fan
thanks: "Code and data are available at: [https://github.com/ycfan0991/popularity_of_childrens_books](https://github.com/ycfan0991/popularity_of_childrens_books)."
date: today
date-format: long
abstract: "This study formulates a predictive model to estimate the popularity of children’s books by the reader’s ratings, physical attributes of the books and yearly trend. The study used a dataset of children’s books that were published from the year 1905 to 2020. The generalized linear model with a log-liner link has been used, where the predictors are publication year, years from first publication, cover type, number of pages and average rating by readers, and the predicted variable is the total count of ratings received from readers as an indicator of popularity. The study found that apart from the average rating, the number of pages in the book has a significant effect on the potential popularity, whereas the cover type of the book has no effect. The study suggests that republishing older children’s books can increase the probability of having higher popularity. The low model fit and lack of availability of data regarding the genre and target audience of the book may limit the reliability of the prediction."
format: pdf
number-sections: true
bibliography: references.bib
---
